project-plan

### 2025-09-25 project-plan.qmd
Adding the Aim

The Swedish Trauma Registry includes patients of all ages who have sustained serious injuries from traumatic events
such as falls, traffic incidents, or other external violence. Since 2024 , patients have been included if a trauma
team activation has occurred, regardless of injury severity, or if they have a New Injury Severity Score (NISS)
greater than fifteen without trauma team activation. Patients transferred to a hospital within seven days of the
traumatic event with a NISS greater than fifteen are also included. Exclusion criteria are cases where the only
traumatic condition is chronic subdural haematoma, trauma alarms without an underlying traumatic event, patients with
protected identity, and patients declared dead on arrival. Since these inclusion and exclusion criteria have changed
over time, patients in this study will be filtered to ensure they fulfil the criteria relevant to the study period
(Källa SweTrau årsbok 2024). <!--Use the 2023 version instead? Data is up to 2023 -->

@@

Setting
---------
Karolinska University Hospital in Solna houses Trauma Centre Karolinska (TCK), Sweden’s largest provider of advanced
trauma care for both adults and children. According to the definition of the American College of Surgeons, Karolinska
University Hospital in Solna serves as the designated Level 1 trauma centre for the greater metropolitan area of
Stockholm. This designation requires around-the-clock availability of key services, including neurosurgery, general
surgery, orthopaedic surgery, anaesthesia and intensive care, as well as diagnostic and interventional radiology and
consultants from other relevant specialities. (Källa   från American College of surgeons, plus källa  som säger NKS
har alla dessa saker). Also, the ICU units in Karolinska Universitets sjukhuset are all recognised as Level 3 units
per the Svenska Föreningen för Anestesi och Intensivvård. (källa )

@@

Patients younger than 18 years were excluded, as their trauma follows separate clinical care systems and quality <!-- is this true? could not fins source-->
review processes that differ from those for adults . Also excluded were patients declared dead on arrival, since
assessment of opportunities for improvement in these cases is not relevant to the aim of this study.

@@

Statistical methods
----------------
<!-- unsure -->

>>>>

The Swedish Trauma Registry includes patients of all ages who have sustained serious injuries from traumatic events
such as falls, traffic incidents, or other external violence. Since 2024 , patients have been included if a trauma
team activation has occurred, regardless of injury severity, or if they have a New Injury Severity Score (NISS)
greater than fifteen without trauma team activation. Patients transferred to a hospital within seven days of the
traumatic event with a NISS greater than fifteen are also included. Exclusion criteria are cases where the only
traumatic condition is chronic subdural haematoma, trauma alarms without an underlying traumatic event, patients with
protected identity, and patients declared dead on arrival. Since these inclusion and exclusion criteria have changed
over time, patients in this study will be filtered to ensure they fulfil the criteria relevant to the study period
(Källa SweTrau årsbok 2024). <!--Use the 2023 version instead? Data used is up to 2023 -->

@@

Setting
---------
Karolinska University Hospital in Solna houses Trauma Centre Karolinska (TCK), Sweden’s largest provider of advanced
trauma care for both adults and children. According to the definition of the American College of Surgeons, Karolinska
University Hospital in Solna serves as the designated Level 1 trauma centre for the greater metropolitan area of
Stockholm. This designation requires around-the-clock availability of key services, including neurosurgery, general
surgery, orthopaedic surgery, anaesthesia and intensive care, as well as diagnostic and interventional radiology and
consultants from other relevant specialities. (Källa   från American College of surgeons, plus källa  som säger NKS
har alla dessa saker). Also, the ICU units in Karolinska Universitets sjukhuset are all recognised as Level 3 units
per the Svenska Föreningen för Anestesi och Intensivvård. (källa)

@@

Patients younger than 18 years were excluded, as their trauma follows separate clinical care systems and quality <!-- is this true? could not find source-->
review processes that differ from those for adults . Also excluded were patients declared dead on arrival, since
assessment of opportunities for improvement in these cases is not relevant to the aim of this study.

@@

Statistical methods
----------------

For continuous variables, medians and interquartile ranges (25th-75th  percentiles) are used. Categorical variables
are presented using the number of patients and their corresponding percentages of the cohort. <!-- If multivariable regression and anlysis will be used, how will we handle missing data? -->

Logistic regression was used to examine the association between patient and process-related factors and OFI. Results
are reported as Odds Ratio (OR) with 95% confidence interval (CI), and a p-value of <0.05 was used as the threshold
for statistical significance. To ensure objectivity, all statistical analyses were initially performed on synthetic
data before being applied to the combined trauma registry and trauma care quality database. Statistical analyses were
conducted in R version x.

<!-- unsure how the statistical model will work, previous papers mention multivariable logistic regression and one Uni/bivariable regression. How does this work? -->
